Enabling the Use of GPU Virtualization in Cloud Environments

### 2015-10-07 paper.tex
fichero de compilacion añadido

OpenStack \cite{OpenStack} is a cloud operating system that provides Infrastructure as a Service (IaaS). 
It is able to control large pools of compute, storage, and networking resources throughout a 
datacenter. All this resources are managed through a dashboard or an API that gives administrators 
control while empowering their users to provision resources through a web interface
or a command-line. 
It supports most available hypervisors and handles provisioning 
and life-cycle management of VMs. 
The OpenStack architecture offers a flexibility to create a custom cloud, with no proprietary hardware
or software requirements and the ability to integrate with legacy systems and third party technologies.

From the HPC perspective, OpenStack offers high performance computing (HPC) configurations using
multiple supported hypervisors and different hardware architectures. However, despite to be able to
specify some extra parameters for special resources like GPUs, choosing a host based on the existence
of a GPU is currently unsupported in OpenStack \cite{OpenStackGPU}.

>>>>

OpenStack~\cite{OpenStack} is a cloud operating system that provides Infrastructure as a Service (IaaS). 
It is able to control large pools of compute, storage, and networking resources throughout a 
datacenter. All these resources are managed through a dashboard or an API that gives administrators 
control while empowering their users to provision resources through a web interface
or a command-line. 
It supports most available hypervisors and handles provisioning 
and life-cycle management of VMs.

The OpenStack architecture offers a flexibility to create a custom cloud, with no proprietary hardware
or software requirements and the ability to integrate with legacy systems and third party technologies.

From the HPC perspective, OpenStack offers high performance computing (HPC) configurations using
multiple supported hypervisors and different hardware architectures. However, despite to be able to
specify some extra parameters for special resources like GPUs, choosing a host based on the existence
of a GPU is currently unsupported in OpenStack~\cite{OpenStackGPU}.
